Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2017-02-03 response_to_reviewers.tex

  % ----------------------------------------------------------------------------------------
  % LETTER CONTENT SECTION
  % ----------------------------------------------------------------------------------------

  \opening{
    \textit{Subject: MEDIA-D-16-00507 - Response to reviewers}\\ \\
    \textbf{Dear Sir or Madam,}}

  We would like to thank the reviewers for their pertinent
  remarks that have increased the quality of the manuscript. Whenever
  possible, the comments of the reviewers have been addressed and
  highlighted in the article.

  Please, find below a point-by-point response to each of the issues raised
  by the reviewers.

@@

      blood hemorrhage following prostate biopsy. Please discuss
      why a pre or a post contrast T1w image is missing from the
      clinical trial that will be using DCE images.}\\
    Maybe it was not entirely clear from the text but the DCE sequence
    used in this work is based on T1w. In other words, the
    pre-contrast acquisition corresponds to the first volumes in the
    sequence before the contrast injection. To avoid confusion, this
    has been clarified in the Material section (p.~15/l.~275).
    Additionally, the risk of blood hemorrhage is discarded since the
    biopsies are carried out after the MRI acquisition.

@@

      patients to the same space may result in loss of
      information. Please comment.}\\
    Our normalization is designed to align the \emph{mean kinetic
      expression}. The mean kinetic expression contains cancer and
    non-cancer kinetic information. Assuming that the amount of cancer
    information (voxels) is much lower than the normal tissue, the use
    of this normalization allows to minimize undersired
    patient-specific (overall-intensity, mean contrast, uptake, ...)
    without affecting the lesion information.

@@

      objective is normalization to be patient and institution
      specific. Please comment how the presented model may be affected
      in a multi-institutional study.}\\
    In line with the previous comment on the use of T1w, we want to
    clarify that DCE is based on T1w sequence.
    Moreover, our method does not rely on any manufacturer/machine-specific settings.

@@

      lesions. Further please comment how this model adds value to
      already established clinical pipeline of detecting prostate
      cancer (PIRADS).}\\
    We have included a new stratified analysis, separating PZ and CG,
    which showed an increase of the classification performance in CG after
    applying our

@@

    normalization method as depicted in Fig.\,8 p.~22.
    The PIRADS v2 emphasizes that DCE-MRI has to be included in
    mp-MRI acquisition to detect small lesions. However, it also warns

@@

    that the benefit is modest. Therefore, the impact of an
    improvement of detection in DCE-MRI can only be evaluated in a
    fully mp-MRI CAD system which is beyond the scope of this paper.
    Indeed, we recently showed, --- Lemaitre,

@@

    Unlike a linear SVM, RF allows to find multiple thresholds,
    leading to a much complex decision boundary for this
    feature. Bootstrapping the samples for each tree allows to cope
    with the over-fitting of each decision trees. Results with SVM
    show no particular improvement in comparison with RF. Therefore,
    we do not
    think that including a linear SVM will be beneficial for the paper
    as are the results provided in the additional material showing.

@@

  \end{enumerate}

  Reviewer \#4:
  \begin{enumerate}
  \item \textbf{The title is misleading and not very scientific and I
      would recommend to remove the second part and reword the first
      part to cover the contents of the paper.}\\
    We are not against changing the title but we would like to take
    advantage of this revision to get the opinion of all reviewers
    regarding this matter.
  \item \textbf{The use of the English language needs some attention:
      get it all proof read.}\\
    As suggested, the manuscript has been corrected by an English editing
    service to ensure a good quality writing. A certificate of the
    service can be provided upon request.
  \item \textbf{What guided biopsy was used: US?}\\
    The guided biopsy was performed with a TRUS. We added this
    statement in p.~15/l.~275.
  \item \textbf{The number of cases seems low. This is mentioned as
      possibly affecting the results and that the limitations might be
      based on the sample size. At the end of section 5 one could draw
      the conclusion that they should do a more extensive study.}\\
    The reviewer is right with the comment, unfortunately due to the
    difficulty on acquiring and annotating this kind of data, we
    cannot provide a larger database at this time. However, a
    statement has been added in the discussions p.~23/l.~396,
    describing this limitation of the study.
  \item \textbf{How would this translate to other types of MRI
      systems: it would be good to see experimental results on this or
      at least some discussion.}\\
    Refer to reviewer \#1 / comment 3 since this is a shared remark.
  \item \textbf{The disappointing performance and large standard
      deviation of the PUN model should be investigated and
      explained.}\\
    A discussion is added in p.~17/l.~320. The original published
    model lacks of
    degrees of freedom. Two additional parameters will
    allow for a better fit. However, we used the original formulation
    in our experiments.
  \item \textbf{There should be a detailed discussion on the results
      to indicate which differences are statistically
      significant. ``Significant'' is mentioned in the conclusions, but
      there is no evidence for this.}\\
    We added a Wilcoxon significance test - see Fig.\,7. Now, the term
    significant is only used for $p<0.05$.
  \item \textbf{The overall results seem poor and this could be
      further discussed.}\\
    It is difficult to compare with the state-of-the-art methods since
    the dataset used are different and the reported results in those
    studies are usually linked to a mp-MRI CAD instead of only
    DCE. Nevertheless, our results are in the same range than Litjens,
    Geert, et al. "Computer-aided detection of prostate cancer in
    MRI." IEEE transactions on medical imaging 33.5 (2014):
    1083-1092 regarding the classification performance of the Tofts
    parameters.
  \item \textbf{Sections 5 and 6 are both disappointingly short.}
    After including the remarks from the reviewers, this section has
    become much longer.
    % However,
    % we believed that there is no need for repeating information
    % already presented in the experiment section or give hypothesis
    % which cannot be verified.
  \item \textbf{Some journals references incomplete. Gliozzi et al. is
      not a single page. Check: Schabel, Shanbhag, Zhu.}\\
    The references have been corrected.
  \end{enumerate}

@@

    This is important to emphasize that our goal was to propose a
    normalization method to allow classification of the entire
    enhanced signal which should perform as good as the current
    models. For the sake of completeness, we apply the same
    normalization on the different

@@

    pharmacokinetic models and, as mentioned by the reviewer ---
    the results are not significantly better as the model parameters
    might have a different interpretation after the normalization is
    applied.

@@

    Indeed, these experiments were carried out to investigate the
    benefit or not of the normalization with the current models.

@@

      individuals does not appear.}\\
    Figure 1 is used to illustrate inter-patients variation in T2w-MRI
    and to highlight the need of a different normalization approach
    than the one needed in T2w. We have clarified in the caption that
    Fig.\,1 is related to T2w, and if requested by the reviewers,
    Figure 1 could be removed. We improve the Fig.\,2. Figure~2(a)

@@

    There is probably a confusion. We do not try to smooth the heatmap
    but we search a smooth estimate. Equation 1 represents the weight
    of the graph and is a standard way to formalize graph-based
    problem in image processing which often includes a data driven
    term and a smoothing term.

@@

      included.}\\
    While other registrations could have been used,
    using a rigid registration directly affect the variations
    $\alpha_i$ and $\Delta_t$. Non rigid registration is deemed not
    necessary as the main parameters that we propose to recover are
    translations and scaling. Moreover, this kind of registration
    might induce deformation artifacts which could impact on the
    overall contrast enhancement over time.

### 2017-02-03 03_experiments/experiments.tex
Update everything

\ac{dce}-\ac{mri} is performed using a fat-suppressed 3D T$_1$ VIBE
sequence (\ac{tr}/\ac{te}/Flip angle:
\SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times
192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); a slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.

>>>>

\ac{dce}-\ac{mri} is performed using a fat-suppressed 3D T$_1$ VIBE
sequence (\ac{tr}/\ac{te}/Flip angle:
\SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times
192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); a slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
A power injector (Medrad, Indianola, USA) is used to provide a bolus
injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of
\SI{0.2}{\ml} Gd-DTPA/kg of body weight.
\textbf{The acquisition starts before the bolus injection to obtain
  pre-contrast volumes.}
